\bf Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-01 paper.tex
fixes to tex for Annalias changes
example titles

\[(\mathbfit{x}-\mathbfit{\mu}) \Sigma^{-1}(\mathbfit{x}-\mathbfit{\mu})^T = 2 (\mathbfit{x}-\mathbfit{\mu}) \Sigma^{-1} = 2\mathbfit{s}P^T
\]

@@

We call points in the projection that are on the curve \(\mathbfit{y}\).
From this we can compute the analog equation for the projection as

@@

\subsection{Robust statistics}\label{robust-statistics}

\subsection{Physics?}\label{physics}

>>>>

\[\nabla (\mathbfit{x}-\mathbfit{\mu}) \Sigma^{-1}(\mathbfit{x}-\mathbfit{\mu})^T = 2 (\mathbfit{x}-\mathbfit{\mu}) \Sigma^{-1} = 2\mathbfit{s}P^T
\]

@@

We call points in the projection that are on the curve \(\mathbfit{y}\),
so that \(\mathbfit{y} = \mathbfit{x}P\) for \(\mathbfit{x}\) on the
\pD{} curve. Then
\(\mathbfit{y} - \mathbfit{\mu}_p = (\mathbfit{x} - \mathbfit{\mu})P = \mathbfit{s} P^T \Sigma P\),
where \(\mathbfit{\mu}_p = \mathbfit{\mu} P\) is the projected mean. We
then substitute
\((\mathbfit{y} - \mathbfit{\mu}_p) (P^T \Sigma P)^{-1}\) for
\(\mathbfit{s}\) in the previous equation. From this we can compute the
analog equation for the projection as

@@

\subsection{Robust statistics: weather
extremes}\label{robust-statistics-weather-extremes}
